Progress Report for CSS 586 Course Project: \\ Modeling Latent Patterns in Music

### 2021-04-26 papers/progress/alex/progress-alex.tex
start working on midi preprocess

\section{Planned Methods and Progress}

@@

@@

\section{Future Work}

>>>>

\section{Planned Methods}

@@

Several choices must be made in how to preprocess MIDI files into training
examples for a neural network. In order to accommodate polyphonic music, we will
convert each MIDI file into a piano roll representation, wherein each instrument
track is a sparse matrix of the velocity values for each of 128 possible pitch
levels at each timestep. Because songs are typically at least a few minutes long
and of widely varying length, we will crop songs into equal-length phrases.

The result of this preprocessing is that each training example will be a 3D
tensor of shape (tracks x notes x ticks).

@@

\section{Progress and Remaining Work}
